Metrics

### 2023-11-19 src/metrics.Rmd
Make box plots

>>>>

### Tables

# Create cols with counts
col_overall <- paste0(
    "Overall\n(n=",
    nrow(df),
    ")"
)
col_agree <- paste0(
    "Agreement\n(n=",
    nrow(df %>% filter(age == "adult" & is_agreed == TRUE)),
    ")"
)
col_recon <- paste0(
    "Reconciliation\n(n=",
    nrow(df %>% filter(age == "adult" & is_recon == TRUE)),
    ")"
)
col_adj <- paste0(
    "Adjudication\n(n=",
    nrow(df %>% filter(age == "adult" & is_adj == TRUE)),
    ")"
)

# Add count to col names
col_rename <- list()
col_rename[[col_overall]] <- "Overall"
col_rename[[col_agree]] <- "Agreement"
col_rename[[col_recon]] <- "Reconciliation"
col_rename[[col_adj]] <- "Adjudication"

# Create table
out %>%
    select(
        Model,
        `PCCC Adult`,
        `PCCC Adult Agreement`,
        `PCCC Adult Reconciliation`,
        `PCCC Adult Adjudication`
    ) %>%
    rename(
         Overall = `PCCC Adult`,
         Agreement = `PCCC Adult Agreement`,
         Reconciliation = `PCCC Adult Reconciliation`,
         Adjudication = `PCCC Adult Adjudication`
    ) %>%
    rename(!!!col_rename)
```

```{r}
out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `PCCC Reconciliation`,
        `PCCC Adjudication`
    ) %>%
    rename(
         All = `PCCC`,
         Agreement = `PCCC Agreement`,
         Reconciliation = `PCCC Reconciliation`,
         Adjudication = `PCCC Adjudication`
    ) %>%
    pivot_longer(
        cols = -Model,
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    mutate(
        Stage = factor(Stage, levels = c(
            "Adjudication",
            "Reconciliation",
            "Agreement",
            "All"
        ))
    ) %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(width = 0.4) +
    stat_summary(
        geom = "label",
        fun.y = min,
        aes(label = sprintf("%1.2f", ..y..)),
        position = position_nudge(y = -0.07),
        size = 2.5
    ) +
    stat_summary(
        geom = "label",
        fun.y = max,
        aes(label = sprintf("%1.2f", ..y..)),
        position = position_nudge(y = 0.06),
        size = 2.5
    ) +
    ylim(0, 1) +
    coord_flip() +
    theme_minimal()
```
